Whats reported in the news?

### 2018-04-10 paper/docs/04_Modelresults_50.Rmd
change plots

p <- radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0) +
  labs(title = "Sentiment scores Jun 2017-March 2018") +
  guides(col = guide_legend(ncol = 1)) +
  theme(legend.position = "right",
        axis.text.x = element_text(size = 10),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggsave(filename = "../figs/sentscore_radar.png", width = 9,
       height = 7,
       plot = p)
```

>>>>

p <- radar %>%
  ggRadar(aes(color=site), 
          rescale = F,
          alpha = 0) +
  labs(title = "") +
  guides(col = guide_legend(ncol = 7)) +
  theme(legend.position = "bottom",
        legend.text = element_text(size=14),
        legend.title = element_text(size=0),
        axis.text.x = element_text(size = 16),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggsave(filename = "../figs/sentscore_radar.png", width = 12,
       height = 10,
       plot = p)
```
